Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-07-11 edubots_surveys.Rnw
Changed to teachers

Despite its (arguably) successful implementation in different higher education institutions, 
over all in the fringes of educational activity, its implementation or deployment is not trivial.
Some authors, for instance \cite{sjostrom2018designing} have proposed a conceptual
architecture for the adoption of teaching-oriented chatbots in higher education.  This
conceptual architecture is based on a systematic literature review of
previous studies, examining the design of chatbots in higher education, as well as making a content 
analysis of student emails and discussion forum posts of
four instances of a Java programming course.  The study outlined
several design considerations; among them, the authors emphasised the
importance of developing chatbots in platforms that students and
educators are familiar with and can easily access (i.e. Facebook
Messenger) which was confirmed with \cite{hobert2019you} and
\cite{fernoagua2018intelligent} studies. In addition, Sj{\"o}str{\"o}m et al. \cite{sjostrom2018designing} 
argued that a conceptualision of learners' questions could aid designers in integrating the appropriate
types of questions that the chatbots should support for different
courses.  Coronado et al. \cite{coronado2018cognitive} proposed agents that store
learning materials to be provided on demand to students, whereas the authors in
\cite{crockett2017predicting} reported on tutoring systems,
which can perform initial assessments of students' understanding and
provide learning material that would advance their understanding to
the next level.

@@

Regarding Gender grouping, both gender agree in their uses, so it seems not relevant at all. When looking at the plot containing the sector differentiation it is interesting ot observe how university professors prefer in a higher proportion to use them for grades and FAQs in comparison with Vocational/High School teachers. This seems reasonable as the frequency of seeing the students is smaller at the University so, automating the grade notification for continuous evaluation could seem much more comfortable using an automated tool than using the traditional platform. Furthermore, the high student/professor ratios that university professors have to deal with could be another reason to have a higher number of them willing to use chatbots for FAQs. This could ameliorate the number of misunderstandings and email overload that so many students might generate.

The results, when grouping by experience, confirm the previous observation that experienced professors are not afraid of changes and are willing to accept new technological challenges, at least, in the same way that younger professors are. From this concrete plot it is interesting as well the fact that very few young/inexperience professors are willing to use chatbots for other uses. This reinforces the hypothesis thrown at the beginning of this section and, as these professors have less experience, they also have less field of view to think about ways of using chatbots.

@@

\begin{itemize}
 \item Professors want to have support from their corresponding institution. This is probably due to the strict European data regulations and to avoid the overhead required to sing up and deleting students from year to year.

 \item Professors need sustainability. The main reason is that implementing changes is expensive in terms of effort and prone to errors in the first years of implementing new procedures, therefore, it is logical that if chatbots or messaging platforms are to be introduced, they want this change to be as permanent as possible.

 \item Keep it Simple. Media interaction requirements are simple and only a 2.4\% is requesting more features. This could be a sign of technological burn out produced by the previous and current courses where, due to the pandemic, the use of computer has increased significantly. 
\end{itemize}
%Olia: be consistent in the terms being used, we refer to teachers, then to professors. I would replace the word "professors" above with the word "teachers".

>>>>

Despite its (arguably) successful implementation in different higher education institutions, 
over all in the fringes of educational activity, not in the actual interaction student-teacher, its implementation or deployment is not trivial.
Some authors, for instance \cite{sjostrom2018designing} have proposed a conceptual
architecture for the adoption of teaching-oriented chatbots in higher education.  This
conceptual architecture is based on a systematic literature review of
previous studies, examining the design of chatbots in higher education, as well as making a content 
analysis of student emails and discussion forum posts of
four instances of a Java programming course.  The study outlined
several design considerations; among them, the authors emphasised the
importance of developing chatbots in platforms that students and
educators are familiar with and can easily access (i.e. Facebook
Messenger) which was confirmed with \cite{hobert2019you} and
\cite{fernoagua2018intelligent} studies. In addition, Sj{\"o}str{\"o}m et al. \cite{sjostrom2018designing} 
argued that a conceptualision of learners' questions could aid designers in integrating the appropriate
types of questions that the chatbots should support for different
courses.  Coronado et al. \cite{coronado2018cognitive} proposed agents that store
learning materials to be provided on demand to students, whereas the authors in
\cite{crockett2017predicting} reported on tutoring systems,
which can perform initial assessments of students' understanding and
provide learning material that would advance their understanding to
the next level.

@@

Regarding Gender grouping, both gender agree in their uses, so it seems not relevant at all. When looking at the plot containing the sector differentiation it is interesting ot observe how university teachers prefer in a higher proportion to use them for grades and FAQs in comparison with Vocational/High School teachers. This seems reasonable as the frequency of seeing the students is smaller at the University so, automating the grade notification for continuous evaluation could seem much more comfortable using an automated tool than using the traditional platform. Furthermore, the high student/teacher ratios that university docents have to deal with could be another reason to have a higher number of them willing to use chatbots for FAQs. This could ameliorate the number of misunderstandings and email overload that so many students might generate.

The results, when grouping by experience, confirm the previous observation that experienced teachers are not afraid of changes and are willing to accept new technological challenges, at least, in the same way that younger teachers are. From this concrete plot it is interesting as well the fact that very few young/inexperience teachers are willing to use chatbots for other uses. This reinforces the hypothesis thrown at the beginning of this section and, as these teachers have less experience, they also have less field of view to think about ways of using chatbots.

@@

\begin{itemize}
 \item Teachers want to have support from their corresponding institution. This is probably due to the strict European data regulations and to avoid the overhead required to sing up and deleting students from year to year.

 \item Teachers need sustainability. The main reason is that implementing changes is expensive in terms of effort and prone to errors in the first years of implementing new procedures, therefore, it is logical that if chatbots or messaging platforms are to be introduced, they want this change to be as permanent as possible.

 \item Keep it Simple. Media interaction requirements are simple and only a 2.4\% is requesting more features. This could be a sign of technological burn out produced by the previous and current courses where, due to the pandemic, the use of computer has increased significantly. 
\end{itemize}
%Olia: be consistent in the terms being used, we refer to teachers, then to professors. I would replace the word "professors" above with the word "teachers". 
% Done (mostly) - JJ
